### 2019-03-03 docs/notebooks/results.Rmd
better explain results in VGG16 section

### Other CNN architectures also show similar effects
To test whether these effects resulted from the architecture of AlexNet or were more general, we repeated the simulations using the VGG16 architecture.

@@

We again saw this effect became stronger the more that the VGG16 architecture was trained.

>>>>

### Other CNN architectures also show similar effects
To test whether these effects resulted from the architecture of AlexNet or were more general, we repeated the simulations using the VGG16 architecture. We again saw a clear difference in set size effects when comparing accuracy of networks performing either feature search or spatial conjunction search.

@@

We also again saw that the set size effect increased, as did difference in accuracy v. set size slopes for feature and spatial conjunction search, as the VGG16 architecture was trained for more epochs.
